Unsupervised embeddings capture latent structure of scientific mobility

### 2020-02-25 paper/current/main.tex
Added correct panel label to clustering figure

We investigate the extent to which geography and language dictate the formation of clusters using \textit{CluSim}~\autocite{gates2019element}.
\textit{CluSim} is a method that calculates the similarity between the cluster results and, for hierarchical clustering, can adjust the relative importance of membership at different levels of the hierarchy with scaling parameter $r$, acting likes ``zooming lens''.  
If $r$ is high, the similarity is based on the lower levels of the deprogram , and when $r$ is low, similarity is based on higher levels dendrogram. 
In fig. \ref{fig:clustering}a, we report three cluster similarity curves (continent, language, language family) with varying scaling parameter r.
As expected, continent plays a major role at higher levels of clustering process (low $r$), language and language family explain the clustering process more at the lower levels (high $r$). 
This suggests that geography, then language, are important factors contributing to the structure of international scientific mobility.

>>>>

We investigate the extent to which geography and language dictate the formation of clusters using \textit{CluSim}~\autocite{gates2019element}.
\textit{CluSim} is a method that calculates the similarity between the cluster results and, for hierarchical clustering, can adjust the relative importance of membership at different levels of the hierarchy with scaling parameter $r$, acting likes ``zooming lens''.  
If $r$ is high, the similarity is based on the lower levels of the dendrogram, and when $r$ is low, similarity is based on higher levels dendrogram. 
In fig. \ref{fig:clustering}b, we report three cluster similarity curves (continent, language, language family) with varying scaling parameter $r$.
As expected, continent plays a major role at higher levels of clustering process (low $r$), language and language family explain the clustering process more at the lower levels (high $r$). 
This suggests that geography, then language, are important factors contributing to the structure of international scientific mobility.
